COVID-19 Closures Negatively Impact Restaurant Revenue and Employment

### 2021-02-22 outputs/paper/paper.Rmd
More writing, pre-colour test

This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into groups, or strata, and subsequently divided into clusters. A random sample is drawn from each stratum and each cluster [@gertler].

@@

#TODO: ADD SENTENCE ABOUT REST OF VARIABLES?

@@

#TODO: talk a bit more about who might have been excluded

@@

#TODO: TALK ABOUT SURVEY NON-RESPONSE AND HOW IT AFFECTS ACCURACY. CITE READINGS. Figure \@ref(fig:nonresponse)

@@

#TODO: TALK ABOUT THE ISSUES WITH SELF-REPORTED INFORMATION. CITE READING.

@@

>>>>

This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into clusters, and subsequently divided into groups, or strata. A random sample is drawn from each cluster and each stratum [@gertler].

@@

@@

Finally, in order to ascertain that the recommendations for each of the findings in this report promote and advance human rights, we highlight the right to work as noted by the Ontario Human Rights Commission (OHRC). In response to the COVID-19 pandemic, the OHRC calls for the upholding of this right by providing special supports to vulnerable groups, including racialized communities and workers in precarious employment. The OHRC recognizes the loss of employment that leads to loss of household income and increased poverty as a direct impact of COVID-19 on vulnerable groups [@ohrc2].

@@

Two types of survey non-response, unit and item non-response, present another limitation. The first, in which an individual refuses to participate, and the second, in which a participant refuses to answer a particular question, might affect the accuracy of inferences if the individuals who participate are systemically different from those who do not [@imai].

@@

A final limitation is the use of self-reported information. A main concern is the incidence of social desirability bias, in which respondents might provide answers they deem socially acceptable, rather than the truth [@imai]. In this experiment, such bias could be present in the answers of Survey 2 which asks respondents about closures. Victims to this type of bias, respondents might have claimed they voluntarily ceased their restaurant operations to limit the spread of COVID-19 when they had not.

@@

Particularly, future research might consider studying the impact of closures on populations made vulnerable by the COVID-19 pandemic. The discrimination against the East Asian community that the pandemic exacerbated [@ohrc1], fueled by sensationalist media reports and mis- and disinformation online, might have targeted restaurant businesses directly. A comprehensive study would reveal further information.
